### 2023-03-04 manuscript.tex
Update README.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/003c9db3c507b7e3b0f010f1c8f579bac7ba666d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4332971966

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/4a0cc6accf8643e836371ea6dcf75962146c372d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/4a0cc6accf8643e836371ea6dcf75962146c372d}{SORTEE-Github-Hackathon/manuscript@4a0cc6a}
on March 4, 2023.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/003c9db3c507b7e3b0f010f1c8f579bac7ba666d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/003c9db3c507b7e3b0f010f1c8f579bac7ba666d}{SORTEE-Github-Hackathon/manuscript@003c9db}
on March 4, 2023.
